Knowledge Representation for Service Robots: Supply and Demand

### 2012-05-13 krs-survey.tex
Mention fluents, situation calculus

We call \emph{situations} all temporal concepts with a non-zero duration,
whereas \emph{events} are durationless temporal concepts.

@@

@@

While representation of events \fxwarning{revient à} to label a timestamp,
representation of actions are more complex since they semantically imply
interactions between concepts. From a taxonomy point of view, actions are a
particular type of event that normaly leads to a situation corresponding to the
action realization.

@@

Making decision based on prediction

@@

>>>>

This introduces the disjunction in time representation between
\emph{situations}, that is, any temporal concept with a non-zero duration, and
\emph{events}, that is, any durationless temporal concept.

Other definitions of a situation do exist, notably in the context of
\emph{situation calculus}~\cite{Levesque1998}, Reiter and Levesque consider a
situation to be an history of actions.

@@

The concept of \emph{fluent} plays another important role for time
representation. Fluents are properties (or \emph{conditions}) that change over
time, like $sees(agent1, apple, t)$.

@@

While representation of events boils down to label a timestamp,
representation of actions are more complex since they semantically imply
interactions between concepts. From a taxonomy point of view, actions are a
particular type of event that normaly leads to a situation corresponding to the
action realization.

@@

@@

Since McCarthy's \emph{Situation Calculus} in 1963, numerous knowledge
representation formalisms dedicated to representation and reasoning about
actions and situation have emerged: besides situation calculs, \emph{fluent
calculus} and \emph{event calculus} are the main ones.
Thielscher~\cite{Thielscher2011}} recently proposed a unification of these
approach in a new \emph{action calculus}.
